exploratory

### 2021-11-03 code/analysis_code/exploratory.Rmd
more edit of exploratory

#check if certain column is factor or not
```{r}
is.factor(data1$Sex)
```

#I want to see how many NA values are there for each column. So, I wrote the following code. For manuscript we dont need it.
```{r}
cbind(
      lapply(
             lapply(data1, is.na)
             , sum)
  )
```
#
#I want to see which columns have NA values
```{r}
df <- as.data.frame(
      cbind(
             lapply(
                   lapply(data1, is.na), sum)
        )
   )
rownames(subset(df, df$V1 != 0))
```
#the mean age and SD of mean age:
```{r}
mean(data1$Age)
sd(data1$Age)
```
#For each age group, whats their percentage?
```{r}
 data1 %>% 
     group_by(Age) %>%
     summarise( percent = 100 * n() / nrow( data1) )

```
#people below 35
```{r}
age_summary = data1 %>% 
     dplyr::filter(Age < 36 ) %>%
     group_by(Age) %>%
     summarise( percent = 100 * n() / nrow( data1) )
print(age_summary)
```

```{r}
df1 = data.frame(age_summary)
summarytable_file = here("results", "summarytable.rds")
saveRDS(df1, file = summarytable_file)
```
#percentage of male and female
```{r}
sex_summary =data1 %>% 
     group_by( Sex ) %>% 
     summarise( percent = 100 * n() / nrow( data1) )
print(sex_summary)
```
```{r}
df2 = data.frame(sex_summary)
summarytable_file = here("results", "summarytable2.rds")
saveRDS(df2, file = summarytable_file)
```

#number of people for each educational category
```{r}
table(data1$`education`)
```
```{r}
sum(data1$'education' == 'Primary')
sum(data1$'education' == 'Secondary')
sum(data1$'education' == 'University Postgraduate degree holder')
sum(data1$'education' == 'University Undergraduate degree holder')
```
#percentage of people for each student category
```{r}
education_summary = data1 %>% 
     group_by( `education` ) %>% 
     summarise( percent = 100 * n() / nrow( data1) )
print(education_summary)
```

@@

#student/worker in the heathcare sector?
```{r}
table(data1$`student/heathworker`)
```

#percentage of student/health worker

@@

#household members?
```{r}
table(data1$`Who do you currently live with in the same household? Please select the number of persons in each age category.: 60 years and above`)
table(data1$`Who do you currently live with in the same household? Please select the number of persons in each age category.: 18 to 59 years`)
table(data1$`Who do you currently live with in the same household? Please select the number of persons in each age category.: 12 to 17 years`)
table(data1$`Who do you currently live with in the same household? Please select the number of persons in each age category.: Less than 12 years`)
```
```{r}
table(data1$`economic_status`)
```
```{r}
sum(data1$'economic_status' == 'High income category')
sum(data1$'economic_status' == 'Low income category')
sum(data1$'economic_status' == 'Lower middle income category')
sum(data1$'economic_status' == 'Upper middle income category ')
```

#percentage of income category?
```{r}
income_summary = data1 %>% 
     group_by( `economic_status` ) %>% 
     summarise( percent = 100 * n() / nrow( data1) )
print(income_summary)
```
```{r}
df4 = data.frame(income_summary)
summarytable_file = here("results", "summarytable4.rds")
saveRDS(df4, file = summarytable_file)
```

```{r}
table(data1$`residence`)
```
```{r}
sum(data1$'residence' == 'A rural place / village')
sum(data1$'residence' == 'A Sub-urban setting / urban slum')
sum(data1$'residence' == 'An urban setting / city / town')
```
#percentage of living setup?
```{r}
residence_summary = data1 %>% 
     group_by( `residence` ) %>% 
     summarise( percent = 100 * n() / nrow( data1) )
print(residence_summary)
```
```{r}
df5 = data.frame(residence_summary)
summarytable_file = here("results", "summarytable5.rds")
saveRDS(df5, file = summarytable_file)
```

```{r}
table(data1$`trusted_source`)
```
#most trusted source?
```{r}
source_summary = data1 %>% 
     group_by( `trusted_source` ) %>% 
     summarise( percent = 100 * n() / nrow( data1) )
print(source_summary)
```
```{r}
df6 = data.frame(source_summary)
summarytable_file = here("results", "summarytable6.rds")
saveRDS(df6, file = summarytable_file)
```

@@

#percentage of work from home or not?
```{r}
work_From_home_or_not_Summary = data1 %>% 
     group_by( `work_from_home` ) %>% 
     summarise( percent = 100 * n() / nrow( data1) )
print(work_From_home_or_not_Summary)
```
```{r}
df7 = data.frame(work_From_home_or_not_Summary)
summarytable_file = here("results", "summarytable7.rds")
saveRDS(df7, file = summarytable_file)
```

#Descriptive analysis for each question?
```{r}
table(data1$`quarantined_or_not`)
```
#Quarantined or not
```{r}
q_or_not_summary = data1 %>% 
     group_by( `quarantined_or_not` ) %>% 
     summarise( percent = 100 * n() / nrow( data1) )
print(q_or_not_summary)
```
```{r}
df8 = data.frame(q_or_not_summary)
summarytable_file = here("results", "summarytable8.rds")
saveRDS(df8, file = summarytable_file)
```

```{r}
table(data1$`infection_status_info`)
```
#correct knowledge of their status
```{r}
test_status_summary = data1 %>% 
     group_by( `infection_status_info` ) %>% 
     summarise( percent = 100 * n() / nrow( data1) )
print(test_status_summary)
```
```{r}
df9 = data.frame(test_status_summary)
summarytable_file = here("results", "summarytable9.rds")
saveRDS(df9, file = summarytable_file)
```
#worried about re-infection
```{r}
worry_level_summary = data1 %>% 
     group_by( `worry_level` ) %>% 
     summarise( percent = 100 * n() / nrow( data1) )
print(worry_level_summary)
```
```{r}
df10 = data.frame(worry_level_summary)
summarytable_file = here("results", "summarytable10.rds")
saveRDS(df10, file = summarytable_file)
```

@@

```{r}
table(data1$`During the past 7 days, have you been observing any of the following preventive measures against COVID-19? (Tick all answers that apply): Social distancing of at least 1.5m`)
```
```{r}
table(data1$`During the past 7 days, have you been observing any of the following preventive measures against COVID-19? (Tick all answers that apply): Wearing face mask`)
```
```{r}
table(data1$`During the past 7 days, have you been observing any of the following preventive measures against COVID-19? (Tick all answers that apply): Hand hygiene (regular handwashing with soap or using hand gel)`)
```
```{r}
table(data1$`During the past 7 days, have you been observing any of the following preventive measures against COVID-19? (Tick all answers that apply): Coughing hygiene (covering mouth when coughing or sneezing)`)
```
```{r}
table(data1$`During the past 7 days, have you been observing any of the following preventive measures against COVID-19? (Tick all answers that apply): None of the above`)
```
```{r}
data1 %>% 
     group_by( `During the past 7 days, have you been observing any of the following preventive measures against COVID-19? (Tick all answers that apply): None of the above` ) %>% 
     summarise( percent = 100 * n() / nrow( data1) )
```

>>>>

#Summary for the main outcome variable
```{r}
summary(data1$infection_status_info)
```

#check if this column is a factor or not
```{r}
is.factor(data1$infection_status_info)
```

#plotting infection_status_info count and save the result
```{r}
plot1 <- ggplot(data = data1) +
    geom_bar(mapping = aes(x = infection_status_info))
plot1
figure_file = here("results","infection_status_info_distribution.png")
ggsave(filename = figure_file, plot=plot1) 
```

#I want to see how many NA values are there for each column. So, I wrote the following code. For manuscript we dont need it.
```{r}
cbind(
      lapply(
             lapply(data1, is.na)
             , sum)
  )
```
#
#I want to see which columns have NA values
```{r}
df <- as.data.frame(
      cbind(
             lapply(
                   lapply(data1, is.na), sum)
        )
   )
rownames(subset(df, df$V1 != 0))
```
#Let's find the mean age and SD of mean age:
```{r}
mean(data1$Age)
sd(data1$Age)
```
#For each age group, whats their percentage?
```{r}
 data1 %>% 
     group_by(Age) %>%
     summarise( percent = 100 * n() / nrow( data1) )

```
#what's the percantage of people below 35 among the participants?
```{r}
age_summary = data1 %>% 
     dplyr::filter(Age < 36 ) %>%
     group_by(Age) %>%
     summarise( percent = 100 * n() / nrow( data1) )
print(age_summary)
```

```{r}
df1 = data.frame(age_summary)
summarytable_file = here("results", "summarytable.rds")
saveRDS(df1, file = summarytable_file)
```
#percentage of male and female among the participants
```{r}
sex_summary =data1 %>% 
     group_by( Sex ) %>% 
     summarise( percent = 100 * n() / nrow( data1) )
print(sex_summary)
```
```{r}
df2 = data.frame(sex_summary)
summarytable_file = here("results", "summarytable2.rds")
saveRDS(df2, file = summarytable_file)
```

#what is the number of people for each educational category among the participants?
```{r}
table(data1$`education`)
```
```{r}
sum(data1$'education' == 'Primary')
sum(data1$'education' == 'Secondary')
sum(data1$'education' == 'University Postgraduate degree holder')
sum(data1$'education' == 'University Undergraduate degree holder')
```
#what is the percentage of people for each eductaion category among the participants?
```{r}
education_summary = data1 %>% 
     group_by( `education` ) %>% 
     summarise( percent = 100 * n() / nrow( data1) )
print(education_summary)
```

@@

#number of student/worker in the heathcare sector among the participants?
```{r}
summary(data1$`student/heathworker`)
```

#percentage of student/health worker among participants?

@@

#household members for each participants?
```{r}
table(data1$`Who do you currently live with in the same household? Please select the number of persons in each age category.: 60 years and above`)
table(data1$`Who do you currently live with in the same household? Please select the number of persons in each age category.: 18 to 59 years`)
table(data1$`Who do you currently live with in the same household? Please select the number of persons in each age category.: 12 to 17 years`)
table(data1$`Who do you currently live with in the same household? Please select the number of persons in each age category.: Less than 12 years`)
```

#What is the number of participants for each type of economic status?
```{r}
summary(data1$`economic_status`)
```
```{r}
sum(data1$'economic_status' == 'High income category')
sum(data1$'economic_status' == 'Low income category')
sum(data1$'economic_status' == 'Lower middle income category')
sum(data1$'economic_status' == 'Upper middle income category ')
```

#what is percentage of each income category?
```{r}
income_summary = data1 %>% 
     group_by( `economic_status` ) %>% 
     summarise( percent = 100 * n() / nrow( data1) )
print(income_summary)
```
```{r}
df4 = data.frame(income_summary)
summarytable_file = here("results", "summarytable4.rds")
saveRDS(df4, file = summarytable_file)
```

#what is the number of participants living in different residence setup?
```{r}
summary(data1$`residence`)
```

```{r}
sum(data1$'residence' == 'A rural place / village')
sum(data1$'residence' == 'A Sub-urban setting / urban slum')
sum(data1$'residence' == 'An urban setting / city / town')
```
#percentage of living setup?
```{r}
residence_summary = data1 %>% 
     group_by( `residence` ) %>% 
     summarise( percent = 100 * n() / nrow( data1) )
print(residence_summary)
```
```{r}
df5 = data.frame(residence_summary)
summarytable_file = here("results", "summarytable5.rds")
saveRDS(df5, file = summarytable_file)
```

#what source the trust the most for COVID-related information?
```{r}
table(data1$`trusted_source`)
```
#percentage of most trusted source?
```{r}
source_summary = data1 %>% 
     group_by( `trusted_source` ) %>% 
     summarise( percent = 100 * n() / nrow( data1) )
print(source_summary)
```
```{r}
df6 = data.frame(source_summary)
summarytable_file = here("results", "summarytable6.rds")
saveRDS(df6, file = summarytable_file)
```

@@

#percentage of participants work from home or not?
```{r}
work_From_home_or_not_Summary = data1 %>% 
     group_by( `work_from_home` ) %>% 
     summarise( percent = 100 * n() / nrow( data1) )
print(work_From_home_or_not_Summary)
```
```{r}
df7 = data.frame(work_From_home_or_not_Summary)
summarytable_file = here("results", "summarytable7.rds")
saveRDS(df7, file = summarytable_file)
```

#number of participants who quarantined or not?
```{r}
table(data1$`quarantined_or_not`)
```
#Percentage of participants Quarantined or not
```{r}
q_or_not_summary = data1 %>% 
     group_by( `quarantined_or_not` ) %>% 
     summarise( percent = 100 * n() / nrow( data1) )
print(q_or_not_summary)
```
```{r}
df8 = data.frame(q_or_not_summary)
summarytable_file = here("results", "summarytable8.rds")
saveRDS(df8, file = summarytable_file)
```

#number of people with their respective infection status?
```{r}
table(data1$`infection_status_info`)
```
#correct knowledge of their status with the percentage?
```{r}
test_status_summary = data1 %>% 
     group_by( `infection_status_info` ) %>% 
     summarise( percent = 100 * n() / nrow( data1) )
print(test_status_summary)
```
```{r}
df9 = data.frame(test_status_summary)
summarytable_file = here("results", "summarytable9.rds")
saveRDS(df9, file = summarytable_file)
```
#worried about re-infection
```{r}
worry_level_summary = data1 %>% 
     group_by( `worry_level` ) %>% 
     summarise( percent = 100 * n() / nrow( data1) )
print(worry_level_summary)
```
```{r}
df10 = data.frame(worry_level_summary)
summarytable_file = here("results", "summarytable10.rds")
saveRDS(df10, file = summarytable_file)
```

@@

#the next code basically summarizes the answers for each question:
```{r}
table(data1$`During the past 7 days, have you been observing any of the following preventive measures against COVID-19? (Tick all answers that apply): Social distancing of at least 1.5m`)
```
```{r}
table(data1$`During the past 7 days, have you been observing any of the following preventive measures against COVID-19? (Tick all answers that apply): Wearing face mask`)
```
```{r}
table(data1$`During the past 7 days, have you been observing any of the following preventive measures against COVID-19? (Tick all answers that apply): Hand hygiene (regular handwashing with soap or using hand gel)`)
```
```{r}
table(data1$`During the past 7 days, have you been observing any of the following preventive measures against COVID-19? (Tick all answers that apply): Coughing hygiene (covering mouth when coughing or sneezing)`)
```
```{r}
table(data1$`During the past 7 days, have you been observing any of the following preventive measures against COVID-19? (Tick all answers that apply): None of the above`)
```
```{r}
data1 %>% 
     group_by( `During the past 7 days, have you been observing any of the following preventive measures against COVID-19? (Tick all answers that apply): None of the above` ) %>% 
     summarise( percent = 100 * n() / nrow( data1) )
```
